ZPY: Open Source Synthetic Data for Computer Vision

### 2021-07-08 docs/paper/paper.tex
more images, references, thanks

\begin{abstract}
Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning. In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data. Built on top of Blender, and designed with modularity and readability in mind.
\end{abstract}

@@

@@

Sim2Real Gap and domain randomization

@@

@@

@@

@@

In our package experiment, we expose two boolean toggles as run function kwargs that are categorized as forms of domain randomization. One toggle enables domain randomization in the lighting space: changing the position and intensity of several lights in the sim. The second toggle enables random HDRIs, which change the appearance of the background in the package images.

@@

Training only on synthetic

Training on mixed synthetic and real

@@

TODO

>>>>

\begin{abstract}
Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning. In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data. Built on top of the popular open source 3D platform Blender. And designed with modularity and readability in mind.
\end{abstract}

@@

Usecases for synthetic data

autonomous vehicles \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}

pose estimation for humans \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}

person re-id \ref{shermeyer2020rareplanes}

detection in overhead satellite imagery \ref{shermeyer2020rareplanes}

pose estimation of satellites in space \ref{kisantal2020satellite}

segmentation of clouds \ref{shermeyer2020rareplanes}

@@

We dive deeper into the effects of training curriculum on synthetic data in \ref{sec:curicculum}.

Sim2Real Gap and domain randomization. We perform an ablation study on different types of domain randomization in \ref{sec:domainrandomization}

@@

Other attempts at open source synthetic data \cite{denninger2019blenderproc} \cite{bpycv}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{results.png}
	\caption{Each type of domain randomization is used to create a fully synthetic dataset, which is used to fine-tune a pre-trained model on the task of package detection. Results of the model on a manually labeled test dataset of real images are compared.}
	\label{fig:results}
\end{figure}

@@

Each individual training run

Details on the training setup: GPU, total training time, total number of sweeps, epoch and batch size.

@@

In our package experiment, we expose boolean toggles as run function kwargs that unlock certain forms of domain randomization. One toggle enables domain randomization in the lighting space: changing the position and intensity of several lights in the sim. The second toggle enables random HDRIs, which change the appearance of the background in the package images. The third toggle enables domain randomization for materials, which changes the appearance of the packages themselves, both the texture as well as the material properties. We perform an ablation study to pick appart the contributions of each type of domain randomization to the performance of a detection model trained on synthetic data with each respective form of domain randomization \ref{fig:results}.

Deeper discussion of results

@@

Training only on Synthetic

ref to rare planes

ref to mixed synthetic data

@@

\section{Thanks}
\label{sec:thanks}

Thanks to Aaron Dant and his team at ASRC Federal for discussions about synthetic data and comments on this paper. Thanks to the developer community of zpy for their feedback and contributions. Thanks to the investors and supporters of Zumo Labs for believing in the future of synthetic data.
